---
title: "Call Center Volume Analysis with Prophet"
author: "Your Name"
date: "`r Sys.Date()`"
draft: true
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

here::i_am("posts/kitchener-phone-queues/R/03_time_series_analysis.Rmd")
```

# Introduction

This analysis examines call center volume data using Facebook's Prophet forecasting tool. The analysis accounts for:

-   Weekly and monthly seasonality patterns

-   Statutory and school holiday effects

-   COVID-19 lockdown periods

# Data Preparation

## Load Required Libraries

```{r libraries}
library(prophet)
library(tidyverse)
library(janitor)
library(here)
library(scales)
library(naniar)
```

## Create Supporting Datasets

Load and prepare the data for analysis. The data includes indicators for holidays and COVID lockdown periods.

```{r data_prep}
# load and prep queue dataset
queue_data <- read_csv(here("posts", "kitchener-phone-queues", "data", "queue_data_clean.csv")) |> 
  add_count(date, name = "metric_count") |> 
  filter(metric_count <= 17) |> 
  filter(date >= "2019-03-01") |> 
  pivot_wider(names_from = "metric", values_from = "value") |> 
  clean_names() 

# Find missing dates in data period
all_dates_in_period <- seq.Date(
  ymd("2019-03-01"), 
  ymd("2023-07-31"), 
  "days"
)

# create missing dates df for binding to prepped Prophet df
missing_dates <- tibble(
  ds = as.Date(setdiff(all_dates_in_period, queue_data$date)),
  y = NA
  )

# load and prep holidays dataset
stat_holidays <- read_csv(here("posts", "kitchener-phone-queues", "data", "holidays.csv")) |> 
  filter(
    date >= ymd("2019-03-01"),
    holiday != "Additional Day"
  ) |> 
  rename(ds = date) |> 
  mutate(
    lower_window = 0,
    upper_window = 0
  )

# create covid lockdown dates tibble to include as one-off holidays
lockdowns <- tribble(
  ~holiday, ~ds, ~ds_upper,
  "lockdown_1", ymd("2020-03-17"), ymd("2020-07-16"),
  "lockdown_2", ymd("2020-12-26"), ymd("2021-02-09"),
  "lockdown_3", ymd("2021-04-08"), ymd("2021-07-15"),
  "lockdown_4", ymd("2022-01-05"), ymd("2022-03-20")
) |> 
  mutate(
    lower_window = 0,
    upper_window = as.integer(ds_upper - ds)
  ) |> 
  select(-ds_upper)

# create March break dates tibble to include as holidays
school_breaks <- tribble(
  ~holiday, ~ds, ~lower_window, ~upper_window,
  "March Break", ymd("2019-03-11"), -30, 6,
  "March Break", ymd("2020-03-16"), -30, 6,
  "March Break", ymd("2021-03-15"), -30, 6,  # original (COVID delay to April)
  "April Break", ymd("2021-04-12"), -30, 6,  # actual
  "March Break", ymd("2022-03-14"), -30, 6,
  "March Break", ymd("2023-03-13"), -30, 6,
  "March Break", ymd("2024-03-11"), -30, 6,
  "Summer Break", ymd("2019-07-01"), -45, 61,
  "Summer Break", ymd("2020-07-01"), -45, 61,
  "Summer Break", ymd("2021-07-01"), -45, 61,
  "Summer Break", ymd("2022-07-01"), -45, 61,
  "Summer Break", ymd("2023-07-01"), -45, 61,
  "Summer Break", ymd("2024-07-01"), -45, 61,
  "Christmas Break", ymd("2019-12-23"), -20, 13,
  "Christmas Break", ymd("2020-12-21"), -20, 13,
  "Christmas Break", ymd("2021-12-20"), -20, 13,
  "Christmas Break", ymd("2022-12-26"), -20, 13,
  "Christmas Break", ymd("2023-12-25"), -20, 13,
)

# consolidate holidays tibble
holidays <- bind_rows(stat_holidays, lockdowns, school_breaks)
```

# Analysis of Calls Presented

## Model Configuration

```{r create-calls-pres-df}
# Prepare calls presented data for Prophet
df_pres <- queue_data |> 
  select(ds = date, y = calls_presented, type_of_day) |> 
  group_by(type_of_day) |> 
  mutate(
    z_score = abs(scale(y)),
    y = if_else(z_score < 3, y, NA) # replace outliers with NA
  ) |> 
  ungroup() |> 
  select(ds, y) |> 
  rbind(missing_dates) |> 
  arrange(ds)
```

Configure the Prophet model with appropriate seasonality settings and external regressors.

```{r model-setup}
# Create prophet model
m_pres <- prophet(df_pres, holidays = holidays, seasonality.mode = "multiplicative")
```

## Model Forecasting

Fit the model and generate forecasts.

```{r fit_and_forecast}
# Create future dataframe for predictions
future <- make_future_dataframe(m_pres, periods = 366)

# Generate forecasts
forecast <- predict(m_pres, future) |> 
  clean_names()
```

## Visualization

### Forecast Plot

```{r forecast_plot}
plot(m_pres, forecast) + add_changepoints_to_plot(m_pres)
```

### Component Plots

```{r component_plots}
# Create component plots
prophet_plot_components(m_pres, forecast)
```

```{r school-breaks-impact}
# First add year to both dataframes
df_with_year <- df_pres |> 
  mutate(year = year(ds))

holidays_with_year <- school_breaks |> 
  mutate(year = year(ds)) |> 
  rename(break_start = ds)

# Then join by year and calculate days until break
df_with_breaks <- df_with_year |> 
  left_join(holidays_with_year, by = "year") |> 
  mutate(days_until_break = as.integer(break_start - ds)) |>
  filter(days_until_break >= -7, days_until_break <= 75)

df_with_breaks |> 
  ggplot(aes(x = days_until_break, y = y)) +
  geom_point(alpha = 0.5) +
  geom_smooth(se = FALSE) +
  facet_wrap(~holiday, scales = "free_y") +
  scale_x_reverse() +  # This reverses the x-axis
  labs(x = "Days Until Break Starts", 
       y = "Calls Presented",
       title = "Call Volumes Leading Up to School Breaks",
       subtitle = "Day 0 = First day of break") +
  theme_minimal()
```

# Analysis of % of Calls Answered Within 30 Seconds

## Model Configuration

```{r create-calls-handled-30-df}
# Prepare  data for Prophet
df_hand30 <- queue_data |> 
  select(ds = date, y = percentage_of_service_level_met_with_abandoned_calls_counted_negatively) |> 
  mutate(
    median_abs_dev = mad(y, na.rm = TRUE),
    median_val = median(y, na.rm = TRUE),
    modified_z = abs(0.6745 * (y - median_val) / median_abs_dev),
    y = if_else(modified_z < 3.5, y, NA) # replace outliers with NA
  ) |> 
  ungroup() |> 
  select(ds, y) |> 
  rbind(missing_dates) |> 
  arrange(ds)

holidays_hand30 <- holidays |> 
  filter(!holiday %in% c("Christmas Break", "March Break", "April Break"))
```

Configure the Prophet model with appropriate seasonality settings and external regressors.

```{r model-setup-hand30}
# Create prophet model
m_hand30 <- prophet(df_hand30, holidays = holidays_hand30, seasonality.mode = "additive")
```

## Model Forecasting

Fit the model and generate forecasts.

```{r forecast-hand30}
# Create future dataframe for predictions
future <- make_future_dataframe(m_hand30, periods = 366)

# Generate forecasts
forecast_hand30 <- predict(m_hand30, future) |> 
  clean_names()
```

## Visualization

### Forecast Plot

```{r forecast_plot-hand30}
plot(m_hand30, forecast_hand30) + add_changepoints_to_plot(m_hand30)
```

### Component Plots

```{r component_plots-hand30}
# Create component plots
prophet_plot_components(m_hand30, forecast_hand30)
```

```{r component_plots-hand30-subset}
m_hand30_sub <- m_hand30

m_hand30_sub$history <- m_hand30_sub$history |> 
  filter(ds >= ymd("2023-08-01"))

forecast_hand30_sub <- forecast_hand30 |> 
  filter(ds >= ymd("2023-08-01"))

# Create component plots
prophet_plot_components(m_hand30_sub, forecast_hand30_sub)

```

```{r break-impact-hand30}
# First add year to both dataframes
df_with_year <- df_hand30 |> 
  mutate(year = year(ds))

# Then join by year and calculate days until break
df_with_breaks <- df_with_year |> 
  left_join(holidays_with_year, by = "year") |> 
  mutate(days_until_break = as.integer(break_start - ds)) |>
  filter(days_until_break >= -7, days_until_break <= 75)

df_with_breaks |> 
  ggplot(aes(x = days_until_break, y = y)) +
  geom_point(alpha = 0.5) +
  geom_smooth(se = FALSE) +
  facet_wrap(~holiday, scales = "free_y") +
  scale_x_reverse() +  # This reverses the x-axis
  labs(x = "Days Until Break Starts", 
       y = "% Answered Within 30 Seconds",
       title = "Service Levels Leading Up to School Breaks",
       subtitle = "Day 0 = First day of break") +
  theme_minimal()
```

# Analysis of % of Calls Abandoned

## Model Configuration

```{r create-calls-aband-df}
# Prepare  data for Prophet
df_aband <- queue_data |> 
  select(ds = date, y = percentage_of_calls_abandoned) |> 
  mutate(
    median_abs_dev = mad(y, na.rm = TRUE),
    median_val = median(y, na.rm = TRUE),
    modified_z = abs(0.6745 * (y - median_val) / median_abs_dev),
    y = if_else(modified_z < 3.5, y, NA) # replace outliers with NA
  ) |> 
  ungroup() |> 
  select(ds, y) |> 
  rbind(missing_dates) |> 
  arrange(ds)

holidays_aband <- holidays |> 
  filter(!holiday %in% c("Christmas Break", "March Break", "April Break"))
```

Configure the Prophet model with appropriate seasonality settings and external regressors.

```{r model-setup-aband}
# Create prophet model
m_aband <- prophet(df_aband, holidays = holidays_aband, seasonality.mode = "additive")
```

## Model Forecasting

Fit the model and generate forecasts.

```{r forecast-aband}
# Create future dataframe for predictions
future <- make_future_dataframe(m_aband, periods = 366)

# Generate forecasts
forecast_aband <- predict(m_aband, future) |> 
  clean_names()
```

## Visualization

### Forecast Plot

```{r forecast_plot-aband}
plot(m_aband, forecast_aband) + add_changepoints_to_plot(m_aband)
```

### Component Plots

```{r component_plots_v2}
# Create component plots
prophet_plot_components(m_aband, forecast_aband)
```

```{r component_plots-subset-aband}
m_hand30_sub <- m_hand30

m_hand30_sub$history <- m_hand30_sub$history |> 
  filter(ds >= ymd("2023-08-01"))

forecast_hand30_sub <- forecast_hand30 |> 
  filter(ds >= ymd("2023-08-01"))

# Create component plots
prophet_plot_components(m_hand30_sub, forecast_hand30_sub)

```

```{r create-lockdown-function}
lockdown_1_dates <- seq.Date(ymd("2020-03-17"), ymd("2020-07-16"), "days")
lockdown_2_dates <- seq.Date(ymd("2020-12-26"), ymd("2021-02-09"), "days")
lockdown_3_dates <- seq.Date(ymd("2021-04-08"), ymd("2021-07-15"), "days")
lockdown_4_dates <- seq.Date(ymd("2022-01-05"), ymd("2022-03-20"), "days")

is_lockdown_date <- function(ds, lockdown_dates) {
  ds <- as.Date(ds)
  return(as.numeric(ds %in% lockdown_dates))
}
```

```{r create-dfs-with-lockdown-columns}
df_pres_lockdowns <- df_pres |> 
  mutate(
    lockdown_1 = is_lockdown_date(ds, lockdown_1_dates),
    lockdown_2 = is_lockdown_date(ds, lockdown_2_dates),
    lockdown_3 = is_lockdown_date(ds, lockdown_3_dates),
    lockdown_4 = is_lockdown_date(ds, lockdown_4_dates)
  )

holidays_no_lockdowns <- holidays |> 
  filter(!grepl("lock", holiday))

future_lockdowns <- future |> 
  mutate(
    lockdown_1 = is_lockdown_date(ds, lockdown_1_dates),
    lockdown_2 = is_lockdown_date(ds, lockdown_2_dates),
    lockdown_3 = is_lockdown_date(ds, lockdown_3_dates),
    lockdown_4 = is_lockdown_date(ds, lockdown_4_dates)
  )
```

```{r model-with-lockdown-regressors}
m_lockdown <- prophet(
  holidays = holidays_no_lockdowns, 
  seasonality.mode = "multiplicative",
  mcmc.samples = 1000
  )
m_lockdown <- add_regressor(m_lockdown, "lockdown_1")
m_lockdown <- add_regressor(m_lockdown, "lockdown_2")
m_lockdown <- add_regressor(m_lockdown, "lockdown_3")
m_lockdown <- add_regressor(m_lockdown, "lockdown_4")
m_lockdown <- fit.prophet(m_lockdown, df_pres_lockdowns)

forecast_lockdown <- predict(m_lockdown, future_lockdowns)
prophet_plot_components(m_lockdown, forecast_lockdown)
```

```{r}
regressor_coefficients(m_lockdown)
```
